Inefficient Concessions and Mediation

### 2017-08-25 draft.tex
add notes.tex to hold work on new result
add revision notes to to-do and fix a typo in draft

\title{Inefficient Concessions and Mediation} 
\author{Kristy Buzard\\
Syracuse University \\
kbuzard@syr.edu\\
\\
Ben Horne\\ 
University of California, San Diego\\
\\}
\date{September 30, 2016}
%To Do : define what is ineffieicncy

@@

In period 0, countries 1 and 2 simultaneously give costly concessions $g_1$ and $g_2$ $\in \mathbb{R} \geq 0$. Concessions are given at cost $C(g_i)$ and benefit the recipient $g_i$, where $i\in\left\{l,h\right\}$. For simplicity, let us initially assume $C(g_i)= g_i$. We will relax this assumption later.

@@

The analysis is conducted with standard Incentive Compatibility and Individual Rationality constraints. Consider the commonly held grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever played forever if Fight is played by any party in any round. This paper will focus on separating equilibria in which high types make use of concessions to identify themselves in hopes of establishing Peace. Because we look at grim trigger punishments, there are essentially only 4 equilibrium combinations of strategies after concessions are given:
1) Both countries play Trust always, 
2) Both play Fight always, 
3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards and 
4) Country 2 plays Fight in round 1 while country 1 plays Trust, which is followed by both countries playing Fight from round 2 onwards.

>>>>

\title{Inefficient Concessions and Mediation} 
\author{Kristy Buzard\\
Syracuse University \\
kbuzard@syr.edu\\
\\
Ben Horne\\ 
University of California, San Diego\\
\\}
\date{\today}
%To Do : define what is ineffieicncy

@@

In period 0, countries 1 and 2 simultaneously give costly concessions $g_1$ and $g_2$ $\in \mathbb{R} \geq 0$. Concessions are given at cost $C(g_i)$ and benefit the recipient $g_i$, where $i\in\left\{l,h\right\}$. For simplicity, we initially assume $C(g_i)= g_i$. We will relax this assumption later.

@@

The analysis is conducted with standard Incentive Compatibility and Individual Rationality constraints. Consider the commonly held grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever if Fight is played by any party in any round. This paper will focus on separating equilibria in which high types make use of concessions to identify themselves in hopes of establishing Peace. Because we look at grim trigger punishments, there are essentially only 4 equilibrium combinations of strategies after concessions are given:
1) Both countries play Trust always, 
2) Both play Fight always, 
3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards and 
4) Country 2 plays Fight in round 1 while country 1 plays Trust, which is followed by both countries playing Fight from round 2 onwards.
